Secure Composition of Robust and Optimising Compilers

### 2024-10-10 tech/main.tex
some proofs

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP]{rtp-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-compo-comp1}{\rtp{\ccSI}{\varClass[_1]}}
    \asm{rtp-compo-comp2}{\rtp{\ccIT}{\varClass[_2]}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-compo}{\rtp{\fncompo{\ccSI}{\ccIT}}{\varClass[_1]\cap\varClass[_2]}}
  \end{goals}
\end{lemma}
\begin{proof}
  \incompleteProof
\end{proof}
The following corollary is a nice consequence of \lemref{rtp-compo}.
\begin{corollary}[\Coqed]{\corollarylabel[Commutativity of RTP]{rtp-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-swappable-comp1}{\rtp{\ccII}{\varClass[_1]}}
    \asm{rtp-swappable-comp2}{\rtp{\ccII[\delta]}{\varClass[_2]}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-swappable1}{\rtp{\fncompo{\ccII}{\ccII[\delta]}}{\varClass[_1]\cap\varClass[_2]}}
    \goal{rtp-swappable2}{\rtp{\fncompo{\ccII[\delta]}{\ccII}}{\varClass[_1]\cap\varClass[_2]}}
  \end{goals}
\end{corollary}
\begin{proof}
  \goalref{rtp-swappable1} and \goalref{rtp-swappable2} are an immediate consequence based on \lemmaref{rtp-compo} with \asmref{rtp-swappable-comp1} and \asmref{rtp-swappable-comp2}, noting the commutativity of set intersection.
\end{proof}

@@

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Universal]{rtp-universal-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig}{\mapUniversalWF{\sim_2}{\trgClass[_1]}}
    \asm{rtp-universal-compo-comp1}{\rtpUniversal{\ccSI}{\mapUniversal{\sim_2}{\trgClass[_1]}}{\sim_1}}
    \asm{rtp-universal-compo-comp2}{\rtpUniversal{\ccIT}{\trgClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-compo}{\rtpUniversal{\fncompo{\ccSI}{\ccIT}}{\trgClass[_1]\cap\trgClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  \incompleteProof
\end{proof}

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Existential]{rtp-existential-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-existential-compo-comp1}{\rtpExistential{\ccSI}{\srcClass[_1]}{\sim_1}}
    \asm{rtp-existential-compo-comp2}{\rtpExistential{\ccIT}{\mapExistential{\sim_1}{\srcClass[_2]}}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-existential-compo}{\rtpExistential{\fncompo{\ccSI}{\ccIT}}{\srcClass[_1]\cap\srcClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  \incompleteProof
\end{proof}

@@

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-Universal]{rtp-universal-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig1}{\mapUniversalWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-universal-compo-wfsig2}{\mapUniversalWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-universal-compo-eq2}{\mapUniversal{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-universal-compo-eq1}{\mapUniversal{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-universal-swappable-comp1}{\rtpUniversal{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-universal-swappable-comp2}{\rtpUniversal{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-swappable1}{\rtpUniversal{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-universal-swappable2}{\rtpUniversal{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  todo
\end{proof}

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-existential]{rtp-existential-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-existential-compo-wfsig1}{\mapExistentialWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-existential-compo-wfsig2}{\mapExistentialWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-existential-compo-eq2}{\mapExistential{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-existential-compo-eq1}{\mapExistential{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-existential-swappable-comp1}{\rtpExistential{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-existential-swappable-comp2}{\rtpExistential{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-existential-swappable1}{\rtpExistential{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-existential-swappable2}{\rtpExistential{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  todo
\end{proof}

if $\sim_1,\sim_2:\irl{I}\to\irl{I}$ are galois, then simpler commutativity

>>>>

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP]{rtp-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-compo-comp1}{\rtp{\ccSI}{\varClass[_1]}}
    \asm{rtp-compo-comp2}{\rtp{\ccIT}{\varClass[_2]}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-compo}{\rtp{\fncompo{\ccSI}{\ccIT}}{\varClass[_1]\cap\varClass[_2]}}
  \end{goals}
\end{lemma}
\begin{proof}
  Unfold \goalref{rtp-compo} and introduce the assumptions. 
  \begin{passumptions}
    \asm{rtp-compo-prop}{\varProperty\in\varClass[_1]\cap\varClass[_2]}
    \asm{rtp-compo-trg-prog}{\srcComponent\in\src{S}}
    \asm{rtp-compo-rsat}{\rsat{\srcComponent}{\varProperty}}
  \end{passumptions}
  What is left to show is:
  \begin{goals}
    \goal{rtp-compo-rsat}{\rsat{\ccIT\lrpars{\ccSI\lrpars{\srcComponent}}}%
                               {\varProperty}}
  \end{goals}
  Apply \asmref{rtp-compo-comp2} on \goalref{rtp-compo-rsat} and note that due to \asmref{rtp-compo-prop}, $\varProperty\in\varClass[_2]$ also holds.
  \begin{goals}
    \goal{rtp-compo-rsatc}{\rsat{\ccSI\lrpars{\srcComponent}}{\varProperty}}
  \end{goals}
  Similarly, apply \asmref{rtp-compo-comp1} on \goalref{rtp-compo-rsatc} and note that due to \asmref{rtp-compo-prop}, $\varProperty\in\varClass[_1]$ also holds.
  \begin{goals}
    \goal{rtp-compo-rsatp}{\rsat{\srcComponent}{\varProperty}}
  \end{goals}
  \goalref{rtp-compo-rsatp} is resolved by \asmref{rtp-compo-rsat}.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%
The following corollary is a nice consequence of \lemref{rtp-compo}.
\begin{corollary}[\Coqed]{\corollarylabel[Commutativity of RTP]{rtp-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-swappable-comp1}{\rtp{\ccII}{\varClass[_1]}}
    \asm{rtp-swappable-comp2}{\rtp{\ccII[\delta]}{\varClass[_2]}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-swappable1}{\rtp{\fncompo{\ccII}{\ccII[\delta]}}{\varClass[_1]\cap\varClass[_2]}}
    \goal{rtp-swappable2}{\rtp{\fncompo{\ccII[\delta]}{\ccII}}{\varClass[_1]\cap\varClass[_2]}}
  \end{goals}
\end{corollary}
\begin{proof}
  \goalref{rtp-swappable1} and \goalref{rtp-swappable2} are an immediate consequence based on \lemmaref{rtp-compo} with \asmref{rtp-swappable-comp1} and \asmref{rtp-swappable-comp2}, noting the commutativity of set intersection.
\end{proof}

@@

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Universal]{rtp-universal-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig}{\mapUniversalWF{\sim_2}{\trgClass[_1]}}
    \asm{rtp-universal-compo-comp1}{\rtpUniversal{\ccSI}{\mapUniversal{\sim_2}{\trgClass[_1]}}{\sim_1}}
    \asm{rtp-universal-compo-comp2}{\rtpUniversal{\ccIT}{\trgClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-compo}{\rtpUniversal{\fncompo{\ccSI}{\ccIT}}{\trgClass[_1]\cap\trgClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  Unfold \goalref{rtp-universal-compo} and introduce the assumptions. 
  \begin{passumptions}
    \asm{rtp-universal-compo-prop}{\trgProperty\in\trgClass[_1]\cap\trgClass[_2]}
    \asm{rtp-universal-compo-trg-prog}{\srcComponent\in\src{S}}
    \asm{rtp-universal-compo-rsat}{\rsat{\srcComponent}{\mapUniversal{\fncompo{\sim_1}{\sim_2}}{\trgProperty}}}
  \end{passumptions}
  What is left to show is:
  \begin{goals}
    \goal{rtp-universal-compo-rsat}{\rsat{\ccIT\lrpars{\ccSI\lrpars{\srcComponent}}}%
                                         {\trgProperty}}
  \end{goals}
  Apply \asmref{rtp-universal-compo-comp2} on \goalref{rtp-universal-compo-rsat} and note that due to \asmref{rtp-universal-compo-prop}, $\trgProperty\in\trgClass[_2]$ also holds.
  \begin{goals}
    \goal{rtp-universal-compo-rsatc}{\rsat{\ccSI\lrpars{\srcComponent}}{\mapUniversal{\sim_2}{\trgProperty}}}
  \end{goals}
  Similarly, apply \asmref{rtp-universal-compo-comp1} on \goalref{rtp-universal-compo-rsatc} and note that due to \asmref{rtp-universal-compo-prop} and \asmref{rtp-universal-compo-wfsig}, $\trgProperty\in\mapUniversal{\sim_2}{\trgClass[_1]}$ also holds.
  \begin{goals}
    \goal{rtp-universal-compo-rsatp}{\rsat{\srcComponent}{\mapUniversal{\sim_2}{\mapUniversal{\sim_1}{\trgProperty}}}}
  \end{goals}
  Note that $\mapUniversal{\sim_2}{\mapUniversal{\sim_1}{\trgProperty}}=\mapUniversal{\fncompo{\sim_1}{\sim_2}}{\trgProperty}$, and thus \goalref{rtp-universal-compo-rsatp} is resolved by \asmref{rtp-universal-compo-rsat}.
\end{proof}

\begin{lemma}[\Coqed]{\lemmalabel[Composition of RTP-Existential]{rtp-existential-compo}}
  If 
  \begin{assumptions}
    \asm{rtp-existential-compo-comp1}{\rtpExistential{\ccSI}{\srcClass[_1]}{\sim_1}}
    \asm{rtp-existential-compo-comp2}{\rtpExistential{\ccIT}{\mapExistential{\sim_1}{\srcClass[_2]}}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-existential-compo}{\rtpExistential{\fncompo{\ccSI}{\ccIT}}{\srcClass[_1]\cap\srcClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
  \end{goals}
\end{lemma}
\begin{proof}
  Similar to \lemmaref{rtp-universal-compo}.
\end{proof}

@@

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-Universal]{rtp-universal-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-universal-compo-wfsig1}{\mapUniversalWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-universal-compo-wfsig2}{\mapUniversalWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-universal-compo-eq2}{\mapUniversal{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-universal-compo-eq1}{\mapUniversal{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-universal-swappable-comp1}{\rtpUniversal{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-universal-swappable-comp2}{\rtpUniversal{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-universal-swappable1}{\rtpUniversal{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-universal-swappable2}{\rtpUniversal{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  \goalref{rtp-universal-swappable1} and \goalref{rtp-universal-swappable2} are an immediate consequence based on \lemmaref{rtp-universal-compo} with \asmref{rtp-universal-swappable-comp1} and \asmref{rtp-universal-swappable-comp2}, noting the commutativity of set intersection.
\end{proof}

\begin{corollary}[\Coqed]{\lemmalabel[Commutativity of RTP-existential]{rtp-existential-swappable}}
  If 
  \begin{assumptions}
    \asm{rtp-existential-compo-wfsig1}{\mapExistentialWF{\sim_1}{\irlClass[_2]}}
    \asm{rtp-existential-compo-wfsig2}{\mapExistentialWF{\sim_2}{\irlClass[_1]}}
    \asm{rtp-existential-compo-eq2}{\mapExistential{\sim_2}{\irlClass[_1]}=\irlClass[_1]}
    \asm{rtp-existential-compo-eq1}{\mapExistential{\sim_1}{\irlClass[_2]}=\irlClass[_2]}
    \asm{rtp-existential-swappable-comp1}{\rtpExistential{\ccII}{\irlClass[_1]}{\sim_1}}
    \asm{rtp-existential-swappable-comp2}{\rtpExistential{\ccII[\delta]}{\irlClass[_2]}{\sim_2}}
  \end{assumptions}
  then
  \begin{goals}
    \goal{rtp-existential-swappable1}{\rtpExistential{\fncompo{\ccII}{\ccII[\delta]}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_1}{\sim_2}}}
    \goal{rtp-existential-swappable2}{\rtpExistential{\fncompo{\ccII[\delta]}{\ccII}}{\irlClass[_1]\cap\irlClass[_2]}{\fncompo{\sim_2}{\sim_1}}}
  \end{goals}
\end{corollary}
\begin{proof}
  \goalref{rtp-existential-swappable1} and \goalref{rtp-existential-swappable2} are an immediate consequence based on \lemmaref{rtp-existential-compo} with \asmref{rtp-existential-swappable-comp1} and \asmref{rtp-existential-swappable-comp2}, noting the commutativity of set intersection.
\end{proof}
